---
title: "Assigment 7"
author: "laknath Gunathilake"
date: "February 27, 2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
  download.file("http://www.openintro.org/stat/data/nc.RData", destfile = "nc.RData")
  load("nc.RData")
```

On your own

1.Calculate a 95% confidence interval for the average length of pregnancies (weeks) and interpret it in context. Note that since you're doing inference on a single population parameter, there is no explanatory variable, so you can omit the x variable from the function.
```{r}
inference(y = nc$weeks,est = "mean",type = "ci",method = "theoretical")

```

We are 95 percent confident that the average length of a pregnancy is between 38.1528 and 38.5165 weeks

2.Calculate a new confidence interval for the same parameter at the 90% confidence level. You can change the confidence level by adding a new argument to the function: conflevel = 0.90.

```{r}
inference(y = nc$weeks,est = "mean",type = "ci",method = "theoretical", conflevel = 0.90)
```

3.Conduct a hypothesis test evaluating whether the average weight gained by younger mothers is different than the average weight gained by mature mothers.
```{r}
inference(y=nc$weight,x = nc$mature,est = "mean",type = "ht",null = 0,alternative = "twosided",method = "theoretical")
```

Since the p value is over 0.05 we cannot reject the null hyptothesis that the mean difference is 0

4.Now, a non-inference task: Determine the age cutoff for younger and mature mothers. Use a method of your choice, and explain how your method works.
```{r}
library(dplyr)
nc%>%select(mature,mage)%>%group_by(mature)%>%summarize(min(mage),max(mage))
```

My method provides the minimum and and maximum age values for each group (mature and young moms)
This indicates that the age cutoff for young moms is 35 (young mom is if they are between 13 and 34) and mature mom if they are between 35 and 50

5.Pick a pair of numerical and categorical variables and come up with a research question evaluating the relationship between these variables. Formulate the question in a way that it can be answered using a hypothesis test and/or a confidence interval. Answer your question using the inference function, report the statistical results, and also provide an explanation in plain language.

**Research Question**
Is the average Birthweight of premature babies different from the ones who were due in full term

```{r}
inference(y=nc$weight,x = nc$premie,est = "mean",type = "ht",null = 0,alternative = "twosided",method = "theoretical")
```
Since the p values is less than 0.05 we reject the hypothesis and conclude that that the average difference of birthweight between premature and full term babies is not 0.



