---
title: "Week 2 Assigment"
author: "laknath Gunathilake"
date: "January 14, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
source("http://www.openintro.org/stat/data/cdc.R")
```


## NOW ON YOUR OWN

+Make a scatterplot of weight versus desired weight. Describe the relationship between these two variables.

```{r plot}
plot( cdc$weight , cdc$wtdesire  )  
```


The actual weight and desired weight seem to have a strong association between 75 and 275lb. However, this relationship is weaker for those who are above 300lb. Meaning for those who are heavier or obese doesn't have their desired weight.


##-Let's consider a new variable: the difference between desired weight (wtdesire) and current weight (weight).
Create this new variable by subtracting the two columns in the data frame and assigning them to a new object called wdiff.
```{r}
  wdiff = cdc$wtdesire - cdc$weight 
```
#What type of data is wdiff? If an observation wdiff is 0, what does this mean about the person's weight and desired weight

```{r}
  class(wdiff)
```

-integer
-the actual weight and the desired weight are the same-Or a person is weighs exactly how much they want to weigh
-negative wdiff=This means that the actual weight is higher than desired weight (They would hope to loose weight)
-positive wdiff=This means that the the actual weight is lower than the desired weight (they would hope to gain weight)

##Describe the distribution of wdiff in terms of its center, shape, and spread, including any plots you use.

```{r}
    hist(wdiff,breaks = 75,xlim = c(-250,200),ylim = c(0,9000))
    mean(wdiff)
    median(wdiff)
```

-the wdiff slightly left skewed
-wdiff has average desired weight of -14.5 and a median desired weight of -10. Based on this we can conclude that most people are unhappy about their weight (they have a lower desired weight than their current weight)

#Using  mumerical summaries and a side-by-side box plot, determine if men tend to view their weight differently than women.

```{r}
  boxplot(cdc$weight~cdc$gender)
  summary(cdc$weight)
  tapply(cdc$weight,cdc$gender, mean, na.rm=TRUE)
  tapply(cdc$weight,cdc$gender, median, na.rm=TRUE)
```

-Men tend to have a higher desired weight than women. 

