---
title: "Week 2 Assigment"
author: "laknath Gunathilake"
date: "January 15, 2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
source("http://www.openintro.org/stat/data/cdc.R")
```


## NOW ON YOUR OWN

###1. Make a scatterplot of weight versus desired weight. Describe the relationship between these two variables.

```{r plot}
plot( cdc$weight , cdc$wtdesire  )  
```


The actual weight and desired weight seem to have a strong association between 75 and 275lb. However, this relationship is weaker for those who are above 300lb.This would make sense since, we can assume that those who are overweight/obese hope to loose weight, and thus have a desired weight that is lower than their current weight.



###2. Let's consider a new variable: the difference between desired weight (wtdesire) and current weight (weight).
Create this new variable by subtracting the two columns in the data frame and assigning them to a new object called wdiff.
```{r}
  wdiff = cdc$wtdesire - cdc$weight 
```
###3. What type of data is wdiff? If an observation wdiff is 0, what does this mean about the person's weight and desired weight What if wdiff is positive or negative?

```{r}
    class(wdiff)
```
  
  + The class of Data is an Integer
  + the actual weight and the desired weight are the same:or a person weighs exactly how much they want to weigh.
  + negative wdiff=This means that the actual weight is higher than desired weight (They would hope to loose weight)
  + positive wdiff=This means that the the actual weight is lower than the desired weight (they would hope to gain weight)

###4. Describe the distribution of wdiff in terms of its center, shape, and spread, including any plots you use.

```{r}
    hist(wdiff,breaks = 75,xlim = c(-250,200),ylim = c(0,9000))
    mean(wdiff)
    median(wdiff)
    min(wdiff)
    max(wdiff)
    library(moments)
    skewness(wdiff)
```


  + Since median is outlier resistant we can use the median and conclude that the center of desired weight is `r median(wdiff)` lb
  + the wdiff slightly left skewed and this is evident from the skewness score of `r skewness(wdiff)`
  + wdiff has mean desired weight of -14.5 and a median desired weight of -10. Based on this we can conclude that most people are unhappy about        their weight (They hope to have a weight lower than their current weight)

### 5.Using  mumerical summaries and a side-by-side box plot, determine if men tend to view their weight differently than women.

```{r}
  boxplot(cdc$wtdesire~cdc$gender,col=(c("blue","pink")))
  tapply(cdc$wtdesire,cdc$gender, mean, na.rm=TRUE)
  tapply(cdc$wtdesire,cdc$gender, median, na.rm=TRUE)
```

 + It is evident that men tend to have a higher desired weight on average than women. On average, men seem to be want to be around 178lb while women    hope to be around the 133lb mark. 

### 6.Now it's time to get creative. Find the mean and standard deviation of weight and determine what proportion of the weights are within one standard deviation of the mean.

```{r}
mean(cdc$weight)
sd(cdc$weight)

within_one_negative<-mean(cdc$weight)-sd(cdc$weight)
within_one_positive<-mean(cdc$weight)+sd(cdc$weight)

within_one_sd<-cdc$weight[ cdc$weight >= within_one_negative & cdc$weight <= within_one_positive]
length(within_one_sd)/length(cdc$weight)*100

```

  + 70 percents of the weights are within one standard deviation of the mean weight which is`r mean(cdc$weight)` 